Tesseroids: forward modeling gravitational fields in spherical coordinates

### 2015-03-07 manuscript.tex
Replace hrefs with urls

\address{
    \noindent
    \footnotemark[1]Universidade do Estado do Rio de Janeiro,
    Rio de Janeiro, Brazil.
    email: leouieda@gmail.com
    \footnotemark[2]Observat\'orio Nacional,
    Rio de Janeiro, Brazil.
}

@@

We have implemented the calculation of
the tesseroid gravitational fields
with adaptive discretization
in version 1.2 of the open-source package \textit{Tesseroids}.
It is freely available online
through a persistent archive\footnote{
\href{}{\todo[inline]{Zenodo DOI}}}
or the software website\footnote{
\href{http://tesseroids.leouieda.com}{http://tesseroids.leouieda.com}}.
The software is distributed under the BSD 3-clause open-source license.
An archived version of the source code
is also available as part of this article.

@@

All figures and numerical experiments in this article
were produced in IPython notebooks\footnote{
\href{http://ipython.org}{http://ipython.org}}
\citep{Perez2007}.
These files combine the analysis and figure generation source code
with text, equations, and the figures generated by the code.
We used the libraries
\textit{pandas} by \citet{Mckinney2010}
to perform the data analysis,
\textit{matplotlib} by \citet{Hunter2007} for graphs,
and \textit{Mayavi} by \citet{Ramachandran2011} for 3D graphs.

The notebook files,
as well as instructions for installing and running the analysis,
are distributed along with the source code archive
that accompanies this article.
Alternatively,
all accompanying material can be downloaded
from an online source code repository\footnote{
\href{https://github.com/pinga-lab/paper-tesseroids}{https://github.com/pinga-lab/paper-tesseroids}}
or a persistent archive\footnote{
\href{}{\todo[inline]{Replace with the Zenodo/figshare DOI for the repository.}}}.

>>>>

\address{
\footnotemark[1]Universidade do Estado do Rio de Janeiro,
Rio de Janeiro, Brazil.
email: leouieda@gmail.com
\footnotemark[2]Observat\'orio Nacional,
Rio de Janeiro, Brazil.
}

@@

We have implemented the calculation of
the tesseroid gravitational fields
with adaptive discretization
in version 1.2 of the open-source package \textit{Tesseroids}.
It is freely available online\footnote{
\url{http://tesseroids.leouieda.com}}\footnote{
\url{}\todo[inline]{Zenodo DOI}}
under the BSD 3-clause open-source license.
An archived version of the source code
is also available as part of this article.

@@

All figures and numerical experiments in this article
were produced in IPython notebooks\footnote{
\url{http://ipython.org}}
\citep{Perez2007}.
These files combine the analysis and figure generation source code
with text, equations, and the figures generated by the code.
We used the libraries
\textit{pandas} by \citet{Mckinney2010}
to perform the data analysis,
\textit{matplotlib} by \citet{Hunter2007} for graphs,
and \textit{Mayavi} by \citet{Ramachandran2011} for 3D graphs.

The notebook files,
as well as instructions for installing and running the analysis,
are distributed along with
the source code archive that accompanies this article.
Alternatively,
all accompanying material is also available online\footnote{
\url{https://github.com/pinga-lab/paper-tesseroids}}\footnote{
\url{}\todo[inline]{Replace with the Zenodo/figshare DOI for the repository.}}.
